*cellcount*: an open-source and automated approach to cyanobacteria enumeration

### 2023-03-03 manuscript_files/draft_manuscript.Rmd
Updates to files

(INSERT IMAGES OF *input_data* SHINY APP HERE)

@@

(INSERT IMAGE OF *analyze_images* SHINY APP HERE)

>>>>

![Graphical user interface of the 'input_data' function using Shiny](C:/Users/Tyler.Harman/Pictures/cellcount-UI_1.png)

@@

![Graphical user interface of the 'analyze_images' function using Shiny](C:/Users/Tyler.Harman/Pictures/cellcount-UI_2.png)
